Implicit yaddayadda

### 2011-10-10 papers/PLDI2012/implicitization.tex
Typos and remarks

$m$, $\delta$ and $\sigma$ can be defined heuristically.
For instance, one could defined $\sigma$ so that $\sigma(j,k)$ only depends on the
last transition of the path, or else construct it dynamically during the
analysis.

@@

Our improvement consists in a slight modification of the SMT formula we solve in
\ref{sec:guided_multigraph}.
We introduce in this formula Boolean variables $\{d_j, 1 \leq j \leq m\}$, so
that we can easily find in the model which abstract value of the disjunction we
have to choose. The resulting formula that is given to the SMT solver is defined
by $g(p_i)$.
When the formula is satisfiable, we know that the index $j$ of the starting
disjunct that has to be chosen is the one for which the associate Boolean value
$d_j$ is \emph{true} in the model. Then, we can easily compute the value of 
$\sigma(j,k)$, thus know the index of the disjunct to join with.

@@

\begin{algorithm}[!h]
\caption{Disjunctive invariant computation with implicit paths}\label{gulwani2}
\label{algo:disjunctive}
\begin{algorithmic}[1] 
\FORALL {$k \in \{1,..,m\} \setminus \{\delta\}$}
	\STATE $X_{i,k} \gets \perp$
\ENDFOR
\STATE $X_{i,\delta} \gets I_{p_i}$
\WHILE {true}
		\STATE $res \gets SmtSolve\left[g(p_i)\right]$
	\IF {$res = unsat$}
		\STATE \textbf{break}
	\ENDIF
	\STATE Compute the path $\tau_{i,k}$ from $res$ 
	\STATE Take $j \in \{ l | d_l = true\}$ 
	\STATE $X_{i,\sigma(j,k)} \gets X_{i,\sigma(j,k)} \widening (X_{i,\sigma(j,k)} \sqcup \tau_{i,k}(X_{i,j}))$
\ENDWHILE
\end{algorithmic}
\end{algorithm}

>>>>

$m$, $\delta$ and $\sigma$ can be defined heuristically.
For instance, one could define $\sigma$ so that $\sigma(j,k)$ only depends on the
last transition of the path, or else construct it dynamically during the
analysis.

@@

Our improvement consists in a slight modification of the SMT formula we solve in
\ref{sec:guided_multigraph}.
We introduce in this formula Boolean variables $\{d_j, 1 \leq j \leq m\}$, so
that we can easily find in the model which abstract value of the disjunction we
have to choose.
\MM{Le ``we have to choose'' est un peu vague. Tu veux dire ``which
  abstract value of the disjunction has to be chosen to make the
  invariant grow'' ?}
The resulting formula that is given to the SMT solver is defined
by $g(p_i)$.
When the formula is satisfiable, we know that the index $j$ of the starting
disjunct that has to be chosen is the one for which the associate Boolean value
$d_j$ is \emph{true} in the model. Then, we can easily compute the value of 
$\sigma(j,k)$, thus know the index of the disjunct to join with.

@@

\MM{Comment cet algo se place par rapport à l'algo
  \ref{algo:combined} ? Si je comprends bien, la boucle while
  remplace l'algo \ref{algo:computepaths}, et l'initialisation au
  début remplace le début de \ref{algo:combined}. Faudrait rendre ça
  explicite.}
\begin{algorithm}[!h]
\caption{Disjunctive invariant computation with implicit paths}\label{gulwani2}
\label{algo:disjunctive}
\begin{algorithmic}[1] 
\FORALL {$k \in \{1,..,m\} \setminus \{\delta\}$}
	\STATE $X_{i,k} \gets \perp$
\ENDFOR
\STATE $X_{i,\delta} \gets I_{p_i}$
\WHILE {true}
		\STATE $res \gets SmtSolve\left[g(p_i)\right]$
	\IF {$res = unsat$}
		\STATE \textbf{break}
	\ENDIF
	\STATE Compute the path $\tau_{i,k}$ from $res$ 
	\STATE Take $j \in \{ l | d_l = true\}$ 
	\STATE $X_{i,\sigma(j,k)} \gets X_{i,\sigma(j,k)} \widening (X_{i,\sigma(j,k)} \sqcup \tau_{i,k}(X_{i,j}))$
\ENDWHILE
\end{algorithmic}
\end{algorithm}
